The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2021-04-16 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

```{r, echo = TRUE, eval=FALSE}
permutation_test <- function(data1, data2, test_column_num, R) {
  #calculate test statsitic and store it
  z <- z.test(x=data1[ ,test_column_num], y=data2[ ,test_column_num], sigma.x =
                sd(data1[ ,test_column_num]), sigma.y = sd(data2[ ,test_column_num]))
  z <- abs(z$statistic)

>>>>

```{r, echo = TRUE, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=50)}
permutation_test <- function(data1, data2, test_column_num, R) {
  #calculate test statsitic and store it
  z <- z.test(x=data1[ ,test_column_num], y=data2[ ,test_column_num], sigma.x =
                sd(data1[ ,test_column_num]), sigma.y = sd(data2[ ,test_column_num]))
  z <- abs(z$statistic)
